---
title: "GMT Online Games -- Data Cleaning"
date: "Last updated: `r format(Sys.time(), '%B %d, %Y')`"
output: 
  github_document:
    toc: true
---

```{r packages}
library(lubridate)
library(readxl)
library(writexl)
library(magrittr)
library(tidyverse)
```

```{r}
df_to_keep = c(
  "df_to_keep",
  "df_fruit1", "dict_fruit1",
  "df_fruit2", "dict_fruit2",
  "df_fruit3", "dict_fruit3",
  "df_fruit4", "dict_fruit4",
  "df_card1", "dict_card1",
  "df_card2", "dict_card2",
  "df_card3", "dict_card3",
  "df_card4", "dict_card4",
  "df_complex1", "dict_complex1", "df_complex1_summary", "dict_complex1_summary",
  "df_complex2", "dict_complex2", "df_complex2_summary", "dict_complex2_summary",
  "df_complex3", "dict_complex3", "df_complex3_summary", "dict_complex3_summary",
  "df_book1", "dict_book1",
  "df_book2", "dict_book2"
)
```


<!-- ======================================================================= -->


# Fruit Clapping Tasks

```{r}
source("fruit1.R")
source("fruit2.R")
source("fruit3.R")
source("fruit4.R")
```


<!-- ======================================================================= -->


# Card Sorting Tasks

```{r}
source("card1.R")
source("card2.R")
source("card3.R")
source("card4.R")
```


<!-- ======================================================================= -->


# Complex Tasks

```{r}
source("complex1.R")
source("complex2.R")
source("complex3.R")
```

I currently have the code set up to subset the data based on the "Task Switch" rows, and then search within each chunk between those rows for a task name. If there is only one row that matches the task name, then I assume that the name is in the correct chunk and I look for corresponding trials. If there is more than 1 task name or there is no task name (presumably because it somehow got output on the wrong side of the Task Switch row and is in the wrong chunk), then I just output NA and go back and hard code it manually.

In Complex 1, there were 2 instances where I removed an empty row at the end because there was a Task Switch with nothing after, and 1 instance where the name didn't show up in the chunk so I had to code that in.

In Complex 2, there were quite a few instances where I had to hard-code fixes here. There was also one participant (118) with completely wonky data that I couldn't figure out manually, so I left 2 rows for that participant blank.

In Complex 3, the only things I had to hard code were for a few participants where there was a Task Switch at the end of the participant's data set, so I just removed the last task (it was unclear what they were switching to at the very end). 

## Complex 2 Dot to Dot scoring issue

Right now, all the Dot to Dot scores for Complex 2 will be NA, because there's stuff missing from the raw data output. THere's no way for me to count the number of dots connected, and it looks like the back-end code for calculating scores/bonus scores is inconsistent. If the participant did Dot to Dot I can still pull number of stops and duration, but scores will be blank.


<!-- ======================================================================= -->


# Bookkeeping Tasks

```{r}
source("book1.R")
source("book2.R")
```


<!-- ======================================================================= -->


# Export data

```{r export_data}
list(fruit1 = df_fruit1,
     fruit2 = df_fruit2,
     fruit3 = df_fruit3,
     fruit4 = df_fruit4,
     card1 = df_card1,
     card2 = df_card2,
     card3 = df_card3,
     card4 = df_card4,
     complex1 = df_complex1, complex1_summary = df_complex1_summary,
     complex2 = df_complex2, complex2_summary = df_complex2_summary,
     complex3 = df_complex3, complex3_summary = df_complex3_summary,
     book1 = df_book1,
     book2 = df_book2) %>%
  write_xlsx("../data/gmt_clean.xlsx")
```

```{r export_dict}
list(fruit1 = dict_fruit1,
     fruit2 = dict_fruit2,
     fruit3 = dict_fruit3,
     fruit4 = dict_fruit4,
     card1 = dict_card1,
     card2 = dict_card2,
     card3 = dict_card3,
     card4 = dict_card4,
     complex1 = dict_complex1, complex1_summary = dict_complex1_summary,
     complex2 = dict_complex2, complex2_summary = dict_complex2_summary,
     complex3 = dict_complex3, complex3_summary = dict_complex3_summary,
     book1 = dict_book1,
     book2 = dict_book2) %>%
  write_xlsx("../data/gmt_dictionary.xlsx")
```


<!-- ======================================================================= -->


# Session info

```{r session_info, include = TRUE}
sessionInfo()
```